Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-03-10 docs/thesis/chap-advanced_techniques.tex
wrote clusring results work on document

\chapter{Advanced Techniques}
\label{chap-advances_techniques}

\section{Latent Semantic Indexing with Semantic Vectors}

>>>>

\chapter{Further Data Analysis}
\label{chap-data_analysis}

In parallel to the development of $5e^{x+y}$ we perform some analysis over our datasets to have a better understanding of the data. Even though this series of analysis did were not directly introduced into the codebase of the system, they provide valuable insights and allowed us to identify future directions of work.

\section{Clustering}

We used Apache Mahout v0.9 for performing the clustering task. 
The following set of commands were used to create and analyse our dataset:

To convert the solr index to a mahout compatible format (Mahout vector):

\small{{\codefont ./mahout lucene.vector -d <path to solr index>  -o ../results/vectors -t ../results/dict -f math           \_notational\_field -st ../results/dict\_seq -x 20 -md 2 -w TFIDF -n 2}}

To run the canopy clustering on the data:

\small{{\codefont ./mahout canpoy -t1 0.15 -t2 0.1 -i ../results/vectors -o ../results/clustering/canopy -dm org.apache.mahout.common.distance.CosineDistanceMeasure}}

To run k-means algorithm on the resulting canopies:

\small{{\codefont ./mahout kmeans -i ../results/vectors -o ../results/clustering\_kmeans -xm sequential  -c ../results/clustering/canopy -x 50 -cd 0.1 -cl -dm org.apache.mahout.common.distance.CosineDistanceMeasure}}

To get the resulting points with their assigned cluster in a human readable format:
\small{{\codefont ./mahout seqdumper -i ../results/clustering\_kmeans/clusteredPoints/part-m-0 > ../results/clustering\_kmeans/clusteredPoints/cluster-points.txt}}

Since the estimation of a good number of clusters k is a challenging task, we also tried to estimate it  by evaluating intra and inter cluster distances for different values of k. Table \ref{cluster_measurements} shows that around k=500 the inter-cluster distance begins to remain stable and by increasing k to 1024, its value is affected only by less than 1\% indicating that a good k number is around 500.

\begin{longtable}{|c|c|c|}
\hline 
\textbf{K} & \textbf{Average Intra-cluster distance} & \textbf{Average Inter-cluster distance} \\ 
\hline 
2 & 0.916 & 0.376  \\ \hline 
4 & 0.907 & 0.557  \\ \hline 
8 & 0.881 & 0.538  \\ \hline 
16 & 0.859 & 0.628  \\ \hline 
32 & 0.818 & 0.781  \\ \hline 
64 & 0.772 & 0.833  \\ \hline 
128 & 0.732 & 0.910  \\ \hline 
256 & 0.694 & 0.938  \\ \hline 
512 & 0.655 & 0.955  \\ \hline 
1024 & 0.610 & 0.963  \\ \hline 
\caption{Cluster measurements for different values of k}
\label{cluster_measurements}
\end{longtable}

The resulting clusters can help us to identify common structures and further improve our results by either adding frequent structures that are common to a cluster, or by reducing the number of elements to perform comparisons against and allow to speed-up the querying process.
Table \ref{} shows the top terms in 2 different clusters that were identified. By simple inspection, it is possible to identify the first one as a cluster grouping trigonometric expressions (Sines and Cosines) and the second one grouping limits where the variable goes to infinity.

{\footnotesize
\begin{longtable}{|>{\centering\arraybackslash}m{3.5cm}c|>{\centering\arraybackslash}m{3.5cm}c|}
\hline 
\textbf{Term} & \textbf{Relative frequence} & \textbf{Term} & \textbf{Relative frequence} \\ 
\hline 
<mi>cos</mi> <mo></mo>	&0.163661208&		<mi>∞</mi>&	0.233151718\\ \hline 
<mi>cos</mi>&	0.157439621	&	<mo>→</mo> <mi>∞</mi>&	0.108867782\\ \hline 
<mo></mo>&	0.121893736&		<mo>→</mo>&	0.108017583\\ \hline 
<mi>θ</mi>&	0.097241797&		<mo>ARROWS</mo>&	0.105854015\\ \hline 
<mo></mo> <mi>θ</mi>&	0.095168449&		<mo>-</mo> <mi>∞</mi>&	0.105012368\\ \hline 
<mrow> <mi>cos</mi> <mo>⁡</mo> <mi>θ</mi> </mrow>&	0.088535288&		<mrow> <mo>-</mo> <mi>∞</mi> </mrow>&	0.102411785\\ \hline 
<mi>cos</mi> <mo></mo> <mi>θ</mi> &	0.088535288&		<mrow> <mo>+</mo> <mi>∞</mi> </mrow>&	0.055650946\\ \hline 
<mi>sin</mi> <mo></mo>&	0.068049679&		<mo>+</mo> <mi>∞</mi>&	0.055490528\\ \hline 
<mi>sin</mi>&	0.066531563&		<mrow> <mrow> <mo>-</mo> <mi>∞</mi> </mrow>&	0.043459138\\ \hline 
<mrow> <mi>sin</mi> <mo></mo> <mi>θ</mi> </mrow>&	0.032338911&		<mo>,</mo> <mi>∞</mi> & 0.021523067\\ \hline 
<mi>sin</mi> <mo></mo> <mi>θ</mi> &	0.032338911&		<mrow> <mo>(</mo> <mrow> <mrow> <mo>-</mo> <mi>∞</mi> </mrow> &	0.020583379\\ \hline 
<mi>φ</mi>&	0.031248212&		<mi>t</mi> <mo>→</mo>&	0.016400033\\ \hline 
<mi>ϕ</mi>&	0.019359824&		<mrow> <mo>[</mo> <mrow> <mrow> <mo>-</mo> <mi>∞</mi> </mrow>& 0.01478247\\ \hline 
<mi></mi>&	0.018438684&		<mi>t</mi>&	0.014620022\\ \hline 
<mo></mo> <mi>ϕ</mi> & 0.017617149 & <mrow> <mo>$\pm$ </mo ><mi>∞ </mi> </mrow> & 0.014477746\\ \hline 
<mrow> <mrow> <mi>cos</mi> <mo></mo> <mi>θ</mi> </mrow>&	0.016889963& <mo>$\pm$</mo> <mi>$\infty$</mi>& 0.014348642\\ \hline 
<mi>cos</mi> <mo></mo> <mi>ϕ</mi>&	0.016157276	&	<mo>|</mo>&	0.012372129\\ \hline 
<mrow> <mi>cos</mi> <mo></mo> <mi>ϕ</mi> </mrow> &	0.016157276	&	<mo>lim</mo>&	0.012214223\\ \hline 
<mo>φ</mo>&	0.015344056 &		<mi>C</mi>	& 0.010421859\\ \hline 
<mi>α</mi>&	0.014598769 &		<mo>∈</mo>	& 0.009871146\\ \hline

\caption{Top 20 terms for two different identified clusters }
\label{cluster_measurements}
\end{longtable} 
}

### 2014-03-10 docs/thesis/chap-evaluation.tex
wrote clusring results work on document

\section{Quality results}
In this section we are interested in evaluating the quality of the results provided by our system.
The type of queries that $5e^{x+y}$ was designed for, are typical equations that can be found in a physics scientific publication. 
Out main user case is that a user of CDS is interested in finding documents inside the collection whose equations are related to the one that is provided.

The evaluated queries were provided by physics experts working at CERN from their own research topics. The queries were provided in \LaTeX format as the users used them in their own publications.
Table \ref{equations_table} presents the set of queries that were evaluated, and a simple explanation about it. 
Each of the users evaluated the results only for the equations he/she provided. For each of the presented result, the user ranked it as "Strictly Relevant", "Partially Relevant" and "Completely Irrelevant". As all evaluations including human interaction, this scoring is at some level subjective.

@@

\begin{itemize}
\item N : Only notational features over the original expression were used
\item N+S : Notational and structural features over the original expression
\item N+S+NN : Notational and structural features over the original expression and notational features over the normalized string using Mathematica's Simplify function
\end{itemize}

@@

We present results for three metrics: Partial precision (Document either partially relevant or completely relevant) strict precision and discounted cumulative gain ($ \mathrm{DCG_{p}} = \sum_{i=1}^{p} \frac{ 2^{rel_{i}} - 1 }{ \log_{2}(i+1)} $).

\begin{longtable}{|c|c|c|c|}
\hline 
\textbf{Scenario} & \textbf{Top 5} & \textbf{Top 10} & \textbf{Top 20} \\ 
\hline 
N & 0.84 & 0.77 & 0.76 \\ 
\hline 
N+S & 0.89 & 0.83 & 0.74 \\ 
\hline 
N+S+NN & 0.91 & 0.93 & 0.87 \\ 
\hline 
\caption{Loose Precision}
\label{loose_precision}
\end{longtable}

\begin{longtable}{|c|c|c|c|}
\hline 
\textbf{Scenario} & \textbf{Top 5} & \textbf{Top 10} & \textbf{Top 20} \\ 
\hline 
N & 0.73 & 0.57 & 0.46 \\ 
\hline 
N+S & 0.82 & 0.67 & 0.52 \\ 
\hline 
N+S+NN & 0.82 & 0.81 & 0.62 \\ 
\hline 
\caption{Strict Precision}
\label{stric_precision}
\end{longtable}

\begin{longtable}{|c|c|c|c|}
\hline 
\textbf{Scenario} & \textbf{Top 5} & \textbf{Top 10} & \textbf{Top 20} \\ 
\hline 
N & 6.99 & 9.39 & 12.07 \\ 
\hline 
N+S & 7.47 & 10.83 & 13.87 \\ 
\hline 
N+S+NN & 7.53 & 11.61 & 15.80 \\ 
\hline 
\caption{Discounted Cumulative Gain}
\label{loose_precision}
\end{longtable}

\section{Querying Performance}

@@

\begin{longtable}{|c|c|p{2cm}|p{2cm}|p{2cm}|}
\hline 
Feature Set & Total time (sec) & Index Size (kb) & Avg. time per equation & Avg. size of equation (kb) \\ 
\hline 
N & 58 & 13926 & 0.00524 & 1.237 \\ 
\hline 
N+S & 884 & 14438 & 0.0785 & 1.282 \\ 
\hline 
N+S+NN & 1273 & 25780 & 0.113 & 2.345 \\ 
\hline 
N+S+FN & 1377 & 25548 & 0.122 & 2.269 \\ 
\hline
\caption{Indexing performance}
\label{indexing_performance}
\end{longtable}

@@

\begin{longtable}{|>{\centering\arraybackslash}m{3.5cm}|>
{\centering\arraybackslash}m{3cm}|>
{\centering\arraybackslash}m{3cm}|
}
\hline 
Expression Length (Number of leaf nodes)& Angular Distance Time (msec) & Tree Edit Distance Time(msec) \\ \hline 
3 & 0.01195 & 2.65  \\ \hline
8 & 0.0142 & 9.97  \\ \hline
7 & 0.0129 & 9.165  \\ \hline
12 & 0.0194 & 15.15  \\ \hline
18 & 0.0201 & 29.5  \\ \hline
20 & 0.0245 & 27.75  \\ \hline
22 & 0.0264 & 32.4  \\ \hline
24 & 0.02502 & 32.1 \\ \hline

>>>>

\section{Quality results}
In this section we are interested in evaluating the quality of the results provided by our system.
The type of queries that $5e^{x+y}$ was designed for, are typical equations that can be found in a physics scientific publication. 
Our main user case is that a user of CDS is interested in finding documents inside the collection whose equations are related to the one that is provided.

The evaluated queries were provided by physics experts working at CERN from their own research topics. The queries were provided in \LaTeX format as the users used them in their own publications.
Table \ref{equations_table} presents the set of queries that were evaluated, and a simple explanation about each one. 
Each of the users evaluated the results only for the equations he/she provided. For each of the presented result, the user ranked it as "Strictly Relevant", "Partially Relevant" and "Completely Irrelevant". As all evaluations including human interaction, this scoring is at some level subjective.

@@

\begin{itemize}
\item N : Only notational features over the original expression were used
\item N+S : Notational and structural features over the original expression
\item N+S+NN : Notational and structural features over the original expression and notational features over the normalized string using Mathematica's Simplify function
\item N+S+NN (BM25): Same scenario as before but using BM25 similarity function instead of TF-IDF. This scoring function is implemented in Lucene through the class {\codefont BM25Similarity}
\end{itemize}

@@

We present results for three metrics: Partial precision (Document either partially relevant or completely relevant) strict precision and discounted cumulative gain ($ \mathrm{DCG_{p}} = \sum_{i=1}^{p} \frac{ 2^{rel_{i}} - 1 }{ \log_{2}(i+1)} $) which measures, in addition, the order of the results..

\begin{longtable}{|c|c|c|c|}
\hline 
\textbf{Scenario} & \textbf{Top 5} & \textbf{Top 10} & \textbf{Top 20} \\ 
\hline 
N & 0.86 & 0.79 & 0.0.78 \\ 
\hline 
N+S & 0.9 & 0.85 & 0.77 \\ 
\hline 
N+S+NN & 0.92 & 0.94 & 0.88 \\ 
\hline
N+S+NN (BM25) & 0.92 & 0.94 & 0.87 \\ 
\hline

\caption{Loose Precision}
\label{loose_precision}
\end{longtable}

\begin{longtable}{|c|c|c|c|}
\hline 
\textbf{Scenario} & \textbf{Top 5} & \textbf{Top 10} & \textbf{Top 20} \\ 
\hline 
N & 0.76 & 0.61 & 0.50 \\ 
\hline 
N+S & 0.84 & 0.70 & 0.56 \\ 
\hline 
N+S+NN & 0.84 & 0.83 & 0.65 \\ 
\hline 
N+S+NN (BM25) & 0.84 & 0.83 & 0.67 \\ 
\hline

\caption{Strict Precision}
\label{stric_precision}
\end{longtable}

\begin{longtable}{|c|c|c|c|}
\hline 
\textbf{Scenario} & \textbf{Top 5} & \textbf{Top 10} & \textbf{Top 20} \\ 
\hline 
N & 7.17 & 9.81 & 12.00 \\ 
\hline 
N+S & 7.61 & 10.7 & 14.59 \\ 
\hline 
N+S+NN & 7.66 & 11.81 & 16.32 \\ 
\hline 
N+S+NN (BM25) & 7.66 & 11.82 & 16.42 \\ 
\hline
\caption{Discounted Cumulative Gain}
\label{dcg}
\end{longtable}

Results show that for the selected queries, the system performs reasonably well achieving a precision of 0.84 in the top 5 results in the best scenario and 0.65 in the top 20 results. 
Even more important than the absolute values, it is more interesting to see how the addition of structural features and the addition of normalization to the expressions, allows the system to improve its performance reasonably. In the top 20 results there was an increase of 15\% from the N scenario to the N+S+NN one. Also we see that in the case of the top 5 results going from N+S to N+S+NN resulted in the same strict precision of 0.84, it still represented and increase in the DCG metric which means still results were improved. 
A final remark is that there was not a significant difference between the two different similarity functions that were evaluated, and in at least one case, BM25 performed worse than standard tf-idf.

@@

\begin{longtable}{|c|c|>
{\centering\arraybackslash}m{2cm}|>
{\centering\arraybackslash}m{2cm}|>
{\centering\arraybackslash}m{2cm}|}
\hline 
\textbf{Feature Set} & \textbf{Total time (sec)} & \textbf{Index Size (kb)} & \textbf{Avg. time per equation} & \textbf{Avg. size of equation (kb)} \\ 
\hline 
N & 58 & 13926 & 0.00524 & 1.237 \\ 
\hline 
N+S & 884 & 14438 & 0.0785 & 1.282 \\ 
\hline 
N+S+NN & 1273 & 25780 & 0.113 & 2.345 \\ 
\hline 
N+S+FN & 1377 & 25548 & 0.122 & 2.269 \\ 
\hline
\caption{Indexing performance}
\label{indexing_performance}
\end{longtable}

\section{Querying Performance}
Similarly, we were also interested in evaluating how the query performance of the queries was affected with the different scenarios. For this set of queries we used the complete dataset, and evaluated the N and the N+S+NN scenarios for queries of different length.

\begin{longtable}{|>{\centering\arraybackslash}m{5cm}|>
{\centering\arraybackslash}m{4cm}|>
{\centering\arraybackslash}m{4cm}|
}
\hline 
\textbf{Expression Length(Number of characters in MathML)}& \textbf{N} & \textbf{N+S+NN} \\ \hline 
70 & 0.178 & 0.327  \\ \hline
198 & 0.179 & 0.810  \\ \hline
452 & 0.323 & 1.692  \\ \hline
771 & 0.393 & 2.066  \\ \hline

\caption{Query performance in seconds}
\label{query_performance}
\end{longtable}

Table \ref{query_performance} shows that for smaller queries, the querying time increases from an average of 0.178 seconds to 0.327 which represents an increase of 83\%. For the largest evaluated set of queries, the querying time passed from 0.393 to 2.066 seconds which represents an increase of around 425\%. The absolute values, however, show that in the worst case the slower query took a little more than 2 seconds in average which is still acceptable for a specialized search engine.

@@

\begin{longtable}{|>{\centering\arraybackslash}m{5cm}|>
{\centering\arraybackslash}m{4cm}|>
{\centering\arraybackslash}m{4cm}|
}
\hline 
\textbf{Expression Length (Number of leaf nodes)}& \textbf{Angular Distance Time (msec)} & \textbf{Tree Edit Distance Time(msec)} \\ \hline 
3 & 0.01195 & 2.65  \\ \hline
8 & 0.0142 & 9.97  \\ \hline
7 & 0.0129 & 9.165  \\ \hline
12 & 0.0194 & 15.15  \\ \hline
18 & 0.0201 & 29.5  \\ \hline
20 & 0.0245 & 27.75  \\ \hline
22 & 0.0264 & 32.4  \\ \hline
24 & 0.02502 & 32.1 \\ \hline

### 2014-03-10 docs/thesis/chap-technical_considerations.tex
wrote clusring results work on document

\begin{longtable}{|m{3.5cm}|>
{\centering\arraybackslash}m{3cm}|>
{\centering\arraybackslash}m{3cm}|>
{\centering\arraybackslash}m{5cm}|
}
\hline 
\textbf{\LaTeX} & 
\textbf{Presentation MathML} & 
\textbf{Content MathML + Presentation Markups} & 
\textbf{OpenMath}  \\ \hline

@@

\begin{longtable}{|
m{2.8cm}|>{\centering\arraybackslash}
m{2cm}|>{\centering\arraybackslash}
m{1.65cm}|>{\centering\arraybackslash}
m{1.65cm}|>{\centering\arraybackslash}
m{1.65cm}|>{\centering\arraybackslash}
m{1.95cm}|>{\centering\arraybackslash}
m{1.65cm}|>{\centering\arraybackslash}
m{1.65cm}|
}
\hline 
\textbf{Software} & \textbf{Type} & \textbf{Tested version} & \textbf{Input Format(s)} & \textbf{Output Format(s)} & \textbf{Licence Type} & \textbf{Latest Update}  \\
\hline
LaTeXML\cite{latexml} & Standalone Executable &0.7.9alpha & \LaTeX & XML + MathML & Open Source & 13 Feb 2014  \\
\hline
TeX4ht\cite{tex4ht1}\cite{tex4ht2} & Standalone Executable & 2009-01-31-07 & \LaTeX & XML + MathML & Open Source & 11 Jun 2009  \\
\hline
LaTeXmathML\cite{latexmathml} & Javascript Library & 30-October-2007 & \LaTeX & XML + MathML & Open Source & 30 Oct 2007  \\
\hline
Maxtract\cite{maxtract1}\cite{maxtract2} & Standalone Executable & v.1752 & PDF & \LaTeX / Annotated PDF & Free to download & 15 Nov 2012  \\
\hline
InftyReader\cite{infty1}\cite{infty2} & Standalone Executable (On Windows) & 2.9.6.2 & PDF, TIFF, BMP, GIF, PNG & \LaTeX, XML + MathML & Commercial & 22 Dec 2013  \\

@@

\begin{longtable}{|m{2cm}|>
{\centering\arraybackslash}m{2cm}|>
{\centering\arraybackslash}m{1.65cm}|>
{\centering\arraybackslash}m{1.65cm}|>
{\centering\arraybackslash}m{1.65cm}|>
{\centering\arraybackslash}m{1.95cm}|>
{\centering\arraybackslash}m{1.65cm}|>
{\centering\arraybackslash}m{1.65cm}|
}
\hline 
\textbf{CAS} & 
\textbf{Imports MathML} & 
\textbf{Expression normalization} & 
\textbf{Pattern Matching}  &
\textbf{License Type}  &
\textbf{Supported APIs}
\\
\hline
Maple &  Yes & Yes & Yes & Commercial & C, Java, VB \\ \hline
MatLab (Symbolic Math Toolbox) & Experimental & Yes & Yes & Commercial & C/C++, Fortran \\ \hline
Mathematica &  Yes & Yes & Yes & Commercial & C, Java, .NET \\ \hline 
Maxima &  Experimental & Yes & Yes & Open Source  & C++, Java (External Project) \\ \hline
SymPy & No & Yes & Yes & Open Source & Python \\ \hline

>>>>

\begin{longtable}{|>{\centering\arraybackslash}m{3.5cm}|>
{\centering\arraybackslash}m{3cm}|>
{\centering\arraybackslash}m{3cm}|>
{\centering\arraybackslash}m{5cm}|
}
\hline 
\textbf{\LaTeX} & 
\textbf{Presentation MathML} & 
\textbf{Content MathML + Presentation Markups} & 
\textbf{OpenMath}  \\ \hline

@@

\begin{longtable}{|>{\centering\arraybackslash}
m{2.93cm}|>{\centering\arraybackslash}
m{1.8cm}|>{\centering\arraybackslash}
m{1.6cm}|>{\centering\arraybackslash}
m{1.9cm}|>{\centering\arraybackslash}
m{1.6cm}|>{\centering\arraybackslash}
m{1.8cm}|>{\centering\arraybackslash}
m{1.4cm}|
}
\hline 
\small{\textbf{Software}} & \small{\textbf{Type}} & \small{\textbf{Tested version}} & \small{\textbf{Input Format(s)}} & \small{\textbf{Output Format(s)}} & \small{\textbf{Licence Type}} & \small{\textbf{Latest Update}}  \\
\hline
\small{LaTeXML}\cite{latexml} & \small{Standalone Executable} & \small{0.7.9alpha} & \small{\LaTeX} & \small{XML + MathML} & \small{Open Source} & \small{13 Feb 2014}  \\
\hline
\small{TeX4ht}\cite{tex4ht2} & \small{Standalone Executable} & \small{ 2009-01-31-07} & \small{\LaTeX} & \small{XML + MathML} & \small{ Open Source} & \small{11 Jun 2009}  \\
\hline
\small{SnuggleTex}\cite{snuggletex} & \small{Java Library} & \small{1.2.2} & \small{\LaTeX (Small fragments)} & \small{MathML} & \small{Open Source} & \small{24 May 2010}  \\
\hline
\small{LaTeXmathML}\cite{latexmathml} & \small{Javascript Library} & \small{30-October-2007} & \small{\LaTeX} & \small{XML + MathML} & \small{Open Source} & \small{30 Oct 2007}  \\
\hline
\small{Maxtract}\cite{maxtract1}\cite{maxtract2} & \small{Standalone Executable} & \small{v.1752} & \small{PDF} & \small{\LaTeX / Annotated PDF} & \small{Free to download} & \small{15 Nov 2012}  \\
\hline
\small{InftyReader}\cite{infty1}\cite{infty2} & \small{Standalone Executable (On Windows)} & \small{2.9.6.2} & \small{PDF, TIFF, BMP, GIF, PNG} & \small{\LaTeX, XML + MathML} & \small{Commercial} & \small{22 Dec 2013}  \\

@@

\begin{longtable}{|>
{\centering\arraybackslash}m{2cm}|>
{\centering\arraybackslash}m{2.1cm}|>
{\centering\arraybackslash}m{1.9cm}|>
{\centering\arraybackslash}m{1.55cm}|>
{\centering\arraybackslash}m{1.83cm}|>
{\centering\arraybackslash}m{1.95cm}|
}
\hline 
\textbf{\small{CAS}} & 
\textbf{\small{Imports MathML}} & 
\textbf{\small{Expression normalization}} & 
\textbf{\small{Pattern Matching}}  &
\textbf{\small{License Type}}  &
\textbf{\small{Supported APIs}}
\\
\hline
\small{Maple} &  \small{Yes} & \small{Yes} & \small{Yes} & \small{Commercial} & \small{C, Java, VB} \\ \hline
\small{MatLab (Symbolic Math Toolbox)} & \small{Experimental} & \small{Yes} & \small{Yes} & \small{Commercial} & \small{C/C++, Fortran} \\ \hline
\small{Mathematica} & \small{Yes} & \small{Yes} & \small{Yes} & \small{Commercial} & \small{C, Java, .NET} \\ \hline 
\small{Maxima} &  \small{Experimental} & \small{Yes} & \small{Yes} & \small{Open Source} & \small{C++, Java (External Project)} \\ \hline
\small{SymPy} & \small{No} & \small{Yes} & \small{Yes} & \small{Open Source} & \small{Python} \\ \hline
